New Metrics for Assessing Projection Pursuit Indexes, and Guiding Optimisation Choices

### 2024-09-12 jso.qmd
add uncertainty accessment for figure 8

The success rate calculated at each hyper-parameter combination (number
of jellyfish and the maximum number of tries) is presented in
@fig-proportion. As the number of jellyfish and maximum tries increase,
the success rate also increases. For simpler problems (6 dimensions),
small parameter values (20 jellyfishes and a maximum of 50 tries) can
already achieve a high success rate. However, larger parameter values
(i.e. 100 jellyfishes and a maximum of 100 tries) are necessary for
higher-dimensional problems (8, 10, and 12 dimensions). Increasing both
parameters enhances the performance of JSO, but it also extends the
computational time required for the optimisation, which can be
computationally intensive when evaluating the index function (such as
scagnostic indexes) multiple times across numerous iterations.

@@

```{r}
#| label = fig-proportion,
#| fig.width = 6,
#| fig.height = 2.5,
#| fig.align = "center",
#| fig.cap = "Proportion of simulations reaches near-optimal index values in the pipe-finding problem using the holes index. The proportion is calculated based on the number of simulations, out of 50, that achieve an index value within 0.05 of the best-performing simulation. As the dimensionality increases, the proportion of simulations reaching the optimal index value increases."
pipe_sim_best <- sim_pipe_run_best |> 
  group_by(n_jellies, max_tries, d) |>
  summarise(I_best = max(I_max))

@@

pipe_res |> 
  rename(`max # of tries` = max_tries) |>
  ggplot(aes(x = n_jellies, y = proportion, 
             group = interaction(d, `max # of tries`),
             color = d)) + 
  geom_line() + 
  scale_color_brewer(palette = "Dark2", name = "dimension") +
  facet_wrap(vars(`max # of tries`), 
             labeller = "label_both") + 
  theme_bw() + 
  xlab("Number of jellyfish") + 
  ylab("Proportion of success")

>>>>

The success rate calculated at each hyper-parameter combination (number
of jellyfish and the maximum number of tries) is presented in
@fig-proportion. The uncertainty is quantified through 500 bootstrap replicates for each case. As the number of jellyfish and maximum tries increase, the success rate also increases. For simpler problems (6 dimensions),
small parameter values (20 jellyfishes and a maximum of 50 tries) can
already achieve a high success rate. However, larger parameter values
(i.e. 100 jellyfishes and a maximum of 100 tries) are necessary for
higher-dimensional problems (8, 10, and 12 dimensions). Increasing both
parameters enhances the performance of JSO, but it also extends the
computational time required for the optimisation, which can be
computationally intensive when evaluating the index function (such as
scagnostic indexes) multiple times across numerous iterations.

@@

```{r}
#| label = fig-proportion,
#| fig.width = 8,
#| fig.height = 3.5,
#| fig.align = "center",
#| fig.cap = "The proportion of simulations that reach near-optimal index values in the pipe-finding problem using the holes index. The proportion is calculated based on the number of simulations, out of 50, that achieve an index value within 0.05 of the best-performing simulation. To quantify uncertainty, Bootstrap samples with 500 are generated. The thin lines represent the proportion for each of the 500 bootstrap replicates, while the thicker lines represent the mean of these bootstrap samples, connnected by lines. As the dimensionality increases, the proportion of simulations reaching the optimal index value increases."
pipe_sim_best <- sim_pipe_run_best |> 
  group_by(n_jellies, max_tries, d) |>
  summarise(I_best = max(I_max))

@@

res_df <- sim_pipe_run_best |> 
  left_join(pipe_sim_best |> ungroup() |> mutate(case_id = row_number()),
            by = c("n_jellies", "max_tries", "d")) |> 
  ungroup() |> 
  group_split(case_id)

resampling <- function(dt, size = size, replace = TRUE){
  row_id <- sample(1:50, size = size, replace = replace)

  dt |> filter(row_number() %in% row_id) |> 
    mutate(diff = abs(I_max - I_best) < 0.05) |> 
    summarise(proportion = sum(diff) / n()) |> 
    pull(proportion)

res_interval_df <- tibble(df = res_df) |> 
  crossing(rep = 1:500) |> 
  rowwise() |> 
  mutate(proportion = resampling(df, size = 50))

res_quantile <- res_interval_df |> 
  unnest(df) |> 
  group_by(n_jellies, max_tries, case_id, d) |> 
  select(-I_max, -id) |> 
  distinct() |> 
  mutate(d = as.factor(d),
         n_jellies = ifelse(d == 10, n_jellies - 1, n_jellies),
         n_jellies = ifelse(d == 12, n_jellies + 1, n_jellies)) |> 
  rename(`max # of tries` = max_tries)

res_quantile |> 
  ungroup() |> 
  ggplot(aes(x = n_jellies - 0.5, y = proportion, 
             group = d, color = d)) + 
  geom_segment(aes(xend = n_jellies + 0.5), size = 0.05) + 
  geom_segment(aes(x = n_jellies - 1, xend = n_jellies + 1), 
               data = res_quantile |> summarise(proportion = mean(proportion)), 
               size = 2) + 
  geom_line(aes(x = n_jellies), 
               data = res_quantile |> summarise(proportion = mean(proportion)), 
            alpha = 0.3) + 
  scale_color_brewer(palette = "Dark2", name = "dimension") +
  scale_x_continuous(breaks = c(20, 50, 100), labels = c("20", "50", "100")) +
  facet_wrap(vars(`max # of tries`), 
             labeller = "label_both") + 
  theme_bw() +
  theme(panel.grid.minor = element_blank()) + 
  xlab("Number of jellyfish") + 
  ylab("Proportion of success")
```

### 2024-09-12 jso.tex
add uncertainty accessment for figure 8

\begin{tcolorbox}[enhanced jigsaw, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, leftrule=.75mm, rightrule=.15mm, bottomrule=.15mm, bottomtitle=1mm, toptitle=1mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, opacitybacktitle=0.6, breakable, arc=.35mm, titlerule=0mm, toprule=.15mm, opacityback=0, left=2mm, colframe=quarto-callout-note-color-frame, colback=white]

@@

The success rate calculated at each hyper-parameter combination (number
of jellyfish and the maximum number of tries) is presented in
Figure~\ref{fig-proportion}. As the number of jellyfish and maximum
tries increase, the success rate also increases. For simpler problems (6
dimensions), small parameter values (20 jellyfishes and a maximum of 50
tries) can already achieve a high success rate. However, larger
parameter values (i.e.~100 jellyfishes and a maximum of 100 tries) are
necessary for higher-dimensional problems (8, 10, and 12 dimensions).
Increasing both parameters enhances the performance of JSO, but it also
extends the computational time required for the optimisation, which can
be computationally intensive when evaluating the index function (such as
scagnostic indexes) multiple times across numerous iterations.

@@

\caption{\label{fig-proportion}Proportion of simulations reaches
near-optimal index values in the pipe-finding problem using the holes
index. The proportion is calculated based on the number of simulations,
out of 50, that achieve an index value within 0.05 of the
best-performing simulation. As the dimensionality increases, the
proportion of simulations reaching the optimal index value increases.}

>>>>

\begin{tcolorbox}[enhanced jigsaw, colback=white, opacityback=0, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, left=2mm, arc=.35mm, breakable, bottomrule=.15mm, bottomtitle=1mm, colframe=quarto-callout-note-color-frame, rightrule=.15mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, coltitle=black, opacitybacktitle=0.6, toprule=.15mm, titlerule=0mm, leftrule=.75mm]

@@

The success rate calculated at each hyper-parameter combination (number
of jellyfish and the maximum number of tries) is presented in
Figure~\ref{fig-proportion}. The uncertainty is quantified through 500
bootstrap replicates for each case. As the number of jellyfish and
maximum tries increase, the success rate also increases. For simpler
problems (6 dimensions), small parameter values (20 jellyfishes and a
maximum of 50 tries) can already achieve a high success rate. However,
larger parameter values (i.e.~100 jellyfishes and a maximum of 100
tries) are necessary for higher-dimensional problems (8, 10, and 12
dimensions). Increasing both parameters enhances the performance of JSO,
but it also extends the computational time required for the
optimisation, which can be computationally intensive when evaluating the
index function (such as scagnostic indexes) multiple times across
numerous iterations.

@@

\caption{\label{fig-proportion}The proportion of simulations that reach
near-optimal index values in the pipe-finding problem using the holes
index. The proportion is calculated based on the number of simulations,
out of 50, that achieve an index value within 0.05 of the
best-performing simulation. To quantify uncertainty, Bootstrap samples
with 500 are generated. The thin lines represent the proportion for each
of the 500 bootstrap replicates, while the thicker lines represent the
mean of these bootstrap samples, connnected by lines. As the
dimensionality increases, the proportion of simulations reaching the
optimal index value increases.}
